---
title: "Homework 1"
author: "Adam Whalen"
date: "9/19/2020"
output: github_document
---

## Problem 1

```{r setup, message = FALSE}
library(tidyverse)
```

Create a data frame.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "mid", "hi", "hi", "hi"))
  )
```

Take the mean of each variable in the data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numeric and logical variables, but not character or factor.
Try converting to numeric:

```{r numeric_manip, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert logical and factor to numeric, but not character, which you can see by multiplying by the random numerical vector.

```{r numeric_multiply, collapse = TRUE}
as.numeric(pull(prob1_df, samp_gt0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, char_vec)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp) 
```

## Problem 2

Load data set: 

````{r prob2_load}
data("penguins", package = "palmerpenguins")
```

The Penguins data set contains `r nrow(penguins_raw)` observations and `r ncol(penguins_raw)` variables. 
