---
title: "Homework 1"
author: "Adam Whalen"
date: "9/19/2020"
output: github_document
---

## Problem 1

```{r setup, message = FALSE}
library(tidyverse)
```

Create a data frame.

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mid", "mid", "mid", "mid", "hi", "hi", "hi"))
  )
```

Take the mean of each variable in the data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numeric and logical variables, but not character or factor. When I try converting to numeric we see that:

```{r numeric_manip, eval = FALSE}
as.numeric(pull(prob1_df, samp_gt0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I can convert logical and factor to numeric, but not character, which you can see by multiplying by the random numerical vector.

```{r numeric_multiply, collapse = TRUE}
as.numeric(pull(prob1_df, samp_gt0)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, char_vec)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp) 
```

## Problem 2

Load data set: 

````{r prob2_load}
data("penguins", package = "palmerpenguins")
```

The Penguins data set describes different species of penguins and their attributes, including different species such as  `r unique(pull(penguins, species))`, their home islands in Antarctica (`r unique(pull(penguins, island))`), and other variables describing various attributes like bill length and body mass. The set contains `r nrow(penguins)` observations and `r ncol(penguins)` variables. The average flipper length of the penguins in the set is `r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)` millimeters.

Create a scatter plot of flipper length on bill length, by species, and export the plot.
```{r penguin_plot}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point(na.rm = TRUE) + labs(title = "Flipper length and bill length \n by species", x = "Bill length", y = "Flipper length")
```

Finally, export the plot.

```{r plot_export}
ggsave("penguin_plot.png")
```






